%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Operational Technologies (OT) Engineer} % Job title
    {INCI GS YUASA} % Organization
    {Manisa, Türkiye} % Location
    {Dec 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Accomplished \textbf{19\%} increase in operational efficiency by reducing production cycle times, as measured by improved production throughput, through the implementation of a \textbf{Unified Namespace (UNS)} based on \textbf{ISA95} standards.}
        \item {Achieved \textbf{14\%} improvement in data reliability by enhancing real-time data flow through the infrastructure optimization with \textbf{OPC UA}, \textbf{MQTT}, and \textbf{Kafka}, which also led to a 90\% improvement in the response time to customer complaints.}
        \item {Reduced production monitoring delays by \textbf{32\%}, as indicated by faster identification of production anomalies, by designing real-time dashboards in \textbf{Grafana} and \textbf{Node.js} for lead-acid battery manufacturing.}
        \item {Led cost-saving digital transformation initiatives, achieving a \textbf{57\%} reduction in operational expenses, as reflected by decreased overhead costs, by modernizing \textbf{OT/ICS} systems and integrating automation technologies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Lead} % Job title
    {DVD VALVES} % Organization
    {Manisa, Türkiye} % Location
    {Jan 2022 - Nov 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led a TEYDEB project (\$200k funding) managing embedded systems and \textbf{web service} integration for smart irrigation hydrants, using \textbf{Node.js} and \textbf{React}, resulting in \textbf{22\%} improvement  in reporting and accounting services efficiency.}
        \item {Developed control systems for irrigation, improving efficiency by \textbf{18\%} using \textbf{DCS}, as demonstrated by optimized system response times.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {DVD VALVES } % Organization
    {Manisa, Türkiye} % Location
    {Jul 2019 - Dec 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated \textbf{IIoT} systems with the \textbf{Focas} library, improving CNC monitoring accuracy by \textbf{48\%}, as evidenced by enhanced real-time visibility.}
        \item {Optimized \textbf{OEE} analysis tools, increasing efficiency by \textbf{12\%}, by analyzing signals from \textbf{CNC}, \textbf{PLC}, and \textbf{web services}, leading to minimized machine idle times.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time Software Development Engineer} % Job title
    {DVD VALVES} % Organization
    {Manisa, Türkiye} % Location
    {Jul 2018 - Jul 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Achieved \textbf{3x faster production cycle} by automating the welding process with \textbf{PLC} and \textbf{HMI}, as realized by shortened cycle time.}
      \end{cvitems}
    }

%---------------------------------------------------------
%\cventry
% {Project Intern Engineer} % Job title
%{MAN TÜRKİYE} % Organization
%{Ankara, Türkiye} % Location
%{Jun 2018 - Jul 2018} % Date(s)
%{
% \begin{cvitems} % Description(s) of tasks/responsibilities
%  \item {Designed and developed a desktop-based Smart Card Inventory Tracking program using \textbf{C\#} and \textbf{SQL}, improving tracking efficiency by \textbf{20\%}}
%\end{cvitems}
%}

%---------------------------------------------------------
  \cventry
    {Part-Time Project Engineer} % Job title
    {DIMES} % Organization
    {İzmir, Türkiye} % Location
    {Jul 2017 - Jun 2018 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced efficiency by \textbf{4\%} through real-time monitoring with \textbf{PLC} and \textbf{IIoT}, as validated by the reduction in maintenance needs.}
      \end{cvitems}
    }
    \vspace{1mm}

%---------------------------------------------------------
\end{cventries}
